Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-05-07 hotstorage13/main.tex

\author{
Wei Zhang$^{\star}$, Tao Yang$^\star$, Gautham Narayanasamy$^\star$, Hong Tang$^\dagger$ \\
{\normalsize$^\star$ University of California at Santa Barbara}, {\normalsize$^\dagger$Alibaba Inc.}
}

>>>>

\author{
Wei Zhang$^{\star}$, Tao Yang$^\star$, Gautham Narayanasamy$^\star$, and Hong Tang$^\dagger$ \\
{\normalsize$^\star$  University of California at Santa Barbara}, {\normalsize$^\dagger$Alibaba Inc.}
%Wei Zhang, Tao Yang, Gautham Narayanasamy\\
%University of California at Santa Barbara
%\and
%Hong Tang\\
%Alibaba Inc.
}
